SDR enhancement by clouds

### 2024-03-21 article/article.Rmd
Commit 2024-03-21 08:11

In this study, we evaluated the effects of the clouds on the total downward radiation
by studding the occurrences of the cloud enhancement cases, their intensity and their
duration.  The recording of the radiation signal is the one-minute average.  Thus, we
will refer to this time step as a cloud enhancement event (CE).

- available data
  - sky cam
  - chp1
  - cm21
  - cimel
- CSid tool

>>>>

In this study, we evaluated the effects of the clouds on the total downward radiation
by studding the occurrences of the cloud enhancement cases, their intensity, and their
duration.  The recording of the radiation signal is the mean of one-minute. Thus, we
will refer to this time step as a cloud enhancement event (CE).

<!--
- available data
  - sky cam
  - chp1
  - cm21
  - cimel
- CSid tool
-->

### 2024-03-21 article/article.tex
Commit 2024-03-21 08:11

In this study, we evaluated the effects of the clouds on the total downward radiation
by studding the occurrences of the cloud enhancement cases, their intensity and their
duration. The recording of the radiation signal is the one-minute average. Thus, we
will refer to this time step as a cloud enhancement event (CE).

\begin{itemize}
\tightlist
\item
  available data

  \begin{itemize}
  \tightlist
  \item
    sky cam
  \item
    chp1
  \item
    cm21
  \item
    cimel
  \end{itemize}
\item
  CSid tool
\end{itemize}

>>>>

In this study, we evaluated the effects of the clouds on the total downward radiation
by studding the occurrences of the cloud enhancement cases, their intensity, and their
duration. The recording of the radiation signal is the mean of one-minute. Thus, we
will refer to this time step as a cloud enhancement event (CE).
